---
name: Maina Handmaker
#surname: Handmaker
position: "PhD Student"
address: "University of Massachusetts Amherst"
phone: 502.523.1157
www: mainahandmaker.com
email: "mhandmaker@umass.edu"
#twitter: mainahandmaker
#github: mainahandmaker
#linkedin: mainahandmaker
headcolor: 414141
date: "`r format(Sys.time(), '%B %Y')`"
output:
  vitae::awesomecv:
    page_total: true
    show_footer: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(here)
library(vitae)
library(dplyr)
library(kableExtra)
```

```{r functions}
readExcelSheets <- function(filename){
  # read all sheets in .xlsx 
  all <- readxl::excel_sheets(filename)
  
  # import each sheet into a list using readxl::read_excel
  list <- lapply(all, function(x) readxl::read_excel(filename, sheet = x))
  
  # save sheet name for each sheet (list)
  names(list) <- all
  
  # breaks up list and creates a dataframe for each sheet with df names matching sheet names
  list2env(list, envir = .GlobalEnv)
}
```

```{r load data, include = FALSE}
# read in cv data
readExcelSheets(here::here("data", "mch_cv_data.xlsx"))
```

# Education

```{r}
education %>% 
  detailed_entries(what = degree, 
                   when = year, 
                   with = institution, 
                   where = where, 
                   why = details,
                   .protect = TRUE)
```

# Work Experience

```{r}
work %>% 
  detailed_entries(what = role, 
                   when = glue::glue("{start_date}--{end_date}"), 
                   with = institution, 
                   where = where, 
                   why = details,
                   .protect = TRUE)
```

# Research Experience

```{r}
research %>% 
  detailed_entries(what = role, 
                   when = glue::glue("{start_date}--{end_date}"), 
                   with = institution, 
                   where = where,
                   why = details,
                   .protect = TRUE)
```

\newpage
# Grants, Fellowships, and Recognitions
## Total funding raised: $336,764

```{r}
grants %>% 
  detailed_entries(what = funder, 
                   with = what,
                   when = when)
```

# Scientific Publications

Smith, A.D., F. J. Sanders, J. Thibault, D. Carter, **M.C. Handmaker**, and F. Smith. *In review*. South Atlantic Bight -- a Final Stop for Ruddy Turnstones Migrating to the Arctic. Journal of Field Ornithology.

Sanders, F. J., **M. C. Handmaker**, A. S. Johnson, and N. R. Senner (2021). Nocturnal roost on South Carolina coast supports nearly half of Atlantic coast population of Hudsonian Whimbrel Numenius hudsonicus during northward migration. Wader Study 128. [*PDF*.](https://doi.org/10.18194/ws.00228)

Kamm, M. D., T. L. Lloyd-Evans, **M. Handmaker**, and J. M. Reed (2019). A half-century of changes in migratory landbird numbers along coastal Massachusetts. PLOS ONE 14:e0222232. [*PDF*.](https://doi.org/10.1371/journal.pone.0222232)

# Popular Publications

Iglecia, M. and **M. Handmaker**. 2018. *Whimbrels on the Wing*. Esri StoryMap. Publication of the Manomet Shorebird Recovery Program.

**Handmaker, M** and L. Chamberlin. 2017. *Journey of a Semipalmated Sandpiper*. Esri StoryMap. Publication of the Western Hemisphere Shorebird Reserve Network (WHSRN).
*Recognized by Esri one of 18 Favorite Community-Produced Story Maps of 2017, out of 250,000

# Presentations
```{r}
presentations %>% 
  detailed_entries(what = title, 
                   when = year, 
                   with = audience, 
                   where = place,
                   why = details,
                   .protect = TRUE)

```

# Teaching and Outreach
```{r}
teaching %>% 
  detailed_entries(what = role, 
                   when = when, 
                   with = what, 
                   where = with,
                   why = details,
                   .protect = TRUE)

```

# Service and Mentoring
```{r}
service %>% 
  detailed_entries(when = when, 
                   what = with,
                   with = what,
                   why = details,
                   .protect = TRUE)

```

# Professional Development and Relevant Coursework
```{r}
training %>% 
  detailed_entries(when = when,
                what = with,
                with = what,
                .protect = TRUE)

```

# Skills
```{r}
options(knitr.kable.NA = "")

skills %>%
kable(booktabs = TRUE, format = "latex") %>%
kable_styling(full_width = F, font_size = 8, latex_options = "hold_position") %>%
row_spec(0, bold = T)
``` 
